### 2014-02-26 paper/concrete.tex
Add back the necessary thing.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
    Then if \ifc{L} satisfies termination sensitive non-interference,
    then \tar{L} satisfies termination sensitive non-interference.
\end{theorem}

>>>>

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
    If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
    \tar{L} satisfies TSNI.
\end{theorem}
